Prediction of PIK3CA mutation with gene expression

### 2020-04-02 plosOne/plosOne.Rmd
plos template

---
title: "PIK3CA mutation prediction"
output: "github_document"
bibliography: references.bib
---

@@

```{r}
knitr::read_chunk('data.R')
knitr::read_chunk('prediction.R')
knitr::read_chunk('logisticRegression.R')
```

### Purpose

PIK3CA mutation prediction by gene expression data

### Introduction

@@

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. Prediction of PIK3CA mutation was done by gene expression data of TCGA.

@@

RNAseq can be widely used. The mutation status directly predictio
### Dataset

@@

@@

```{r}
library(tidyverse)
train_target <- tibble::tibble(summary(trainSetDiff$PIK3CA_T)) 
test_target <- tibble::tibble(summary(testSetDiff$PIK3CA_T))
target <- bind_cols(train_target, test_target) %>%
  rename(TrainSet = "summary(trainSetDiff$PIK3CA_T)", TestSet = "summary(testSetDiff$PIK3CA_T)")

knitr::kable(target)

@@

### Selecting variable for modeling

### Preprocessing

### Modeling

@@

## Results

### selecting model
Cross-validation 
The model showed best performance at lambda = 0.01 and alpha = 1.0 (Ridge regression).

### Prediction performance

#### performance of each cancer type

#### Important predictors

>>>>

---
title: Prediction of PIK3CA mutation with gene expression
author:
  - name: Jun Kang
    email: jkang.alien@gmail.com
    affiliation: Department of Hospital Pathology, Seoul St. Mary’s Hospital, College of Medicine, The Catholic University of Korea, Seoul, South Korea
    corresponding: jkang.alien@gmail.com

abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

```{r}
knitr::read_chunk('../data.R')
knitr::read_chunk('../prediction.R')
knitr::read_chunk('../logisticRegression.R')
```

# Introduction

A list

- Brevity
- Logic and clarity
- Clean typing

The problem

@@

Breast cancer with PIK3CA mutation has been approved to use PIK3CA inhibitor in hormone receptor positive HER2 negative subtype. @andre_2019_alpelisib_nengljmeda Prediction of PIK3CA mutation was done by gene expression data of TCGA.

@@

RNAseq can be widely used. The mutation status directly predictio

Previous study @way_2018_machine_cellreports

The proposed solution

# Materials and Methods

## Dataset

@@

## Selecting variable for modeling

## Preprocessing

## Modeling

# Results

@@

```{r}
library(tidyverse)
train_target <- tibble::tibble(summary(trainSetDiff$PIK3CA_T)) 
test_target <- tibble::tibble(summary(testSetDiff$PIK3CA_T))
target <- bind_cols(train_target, test_target) %>%
  rename(TrainSet = "summary(trainSetDiff$PIK3CA_T)", TestSet = "summary(testSetDiff$PIK3CA_T)")
knitr::kable(target)

@@

@@

## selecting model
Cross-validation 
The model showed best performance at lambda = 0.01 and alpha = 1.0 (Ridge regression).

## Prediction performance

## performance of each cancer type

## Important predictors

# Discussion

Main message answers the question and main supporting evidence

Critical assessment opinions on 
- any shortcomings in study design  
- limitations in methods
- flaws in analysis
- validity of assumption

Comparison with other studies where inconsistencies are discussed

Conclusions comments on possible biological or clinical implications and suggestions for further research.  
Evaluate the results - not the authors

# References {#references .unnumbered}
